### 2014-10-31 evaluation.tex
edits

>>>>

\begin{table}
\setlength{\tabcolsep}{4pt}
{\sffamily \small
\begin{center}
\begin{tabular} {|l|r|r|r|r|r|r|r|}
\hline
{\bf Benchmark} & {\bf \#T} & {\bf EC} & {\bf CC} & {\bf SC} & {\bf RC} & {\bf MAV} & {\bf RR} \\
\hline
{LWW Reg} & 1 & 2 & 2 & 2 & 0 & 0 & 0 \\
{DynamoDB} & 1 & 3 & 1 & 2 & 0 & 0 & 0 \\
{Bank Account} & 1 & 1 & 1 & 1 & 1 & 0 & 1 \\
{Shopping List} & 1 & 2 & 1 & 1 & 0 & 0 & 0 \\
{Online store} & 4 & 9 & 1 & 0 & 2 & 0 & 1 \\
{Rubis} & 6 & 14 & 2 & 1 & 4 & 2 & 0 \\
{Microblog} & 5 & 13 & 6 & 1 & 6 & 3 & 1 \\
\hline
\end{tabular}
\end{center}
}
\caption{The distribution of classfied contracts. \#T refers to the number of tables in the application.}
\label{tab:ctrts}
\end{table}

The distribution of contracts in these applications is given in
Table~\ref{tab:ctrts}. We see that majority of the operations are classified as
eventually consistent. Typically, causally consistent operations tend to be
reads that require to see operations in the same session or causally preceding
effects. Transactions are useful for maintaining cross-object consistency and
integrity constraints. For example, we maintain foregin key relationship
between tables using RC isolation level on the insertion transaction, and MAV
on the read transaction; if a MAV transaction witnesses the foreign key field
on table, then it \emph{will} witness the corresponding primiary key row in the
referenced table.

RR transaction comes in handy for maintaining the integrity of follow user
functionality in microblog. If user $A$ is followed by $B$, then we add a
\emph{followedBy} edge from $A$ to $B$ and a \emph{following} edge in the other
direction. The integrity constraint is that either both the edges are added, or
none. RR transaction isolation level is used to ensure correctness when
concurrently $A$ blocks $B$, and $B$ follows $A$. By operating on a snapshot of
consistent state, the block user transaction will not be interfered by the
concurrent follow user transaction.

### 2014-10-31 implementation.tex
edits

Compared to the shim layer, summarization in the backing store is more
complicated. The main challenge is that unlike the shim layer, summarization
cannot run as an atomic operation. Summarization in the backing store involves
deleting previously inserted rows and inserting new rows, where each row
corresponds to an effect. It is essential that concurrent client operations are
permitted, but are not allowed to witness the intermediate state of the
summarization process.

To this end, we adopt a novel summarization strategy that builds on the
causality property of the store. Suppose we have a set $O$ of effects on a
object, which when summarized yields a new set of effects $N$. We first
instantiate a summarization marker $s$, and similar to transaction marker, we
do not insert it into the store immediately. We insert the new effects in $N$
with strong consistency, including $s$ as a dependence. Since $s$ is not yet in
the store, effects from $N$ are not made visible to the clients. Then we insert
$s$ with strong consistency, including $O$ as dependence, and finally delete
the rows corresponding to $O$. When the shim layer node witnesses the
summarization marker $s$ on the object, it removes the effects from $O$ from
its cache. But due to strong consistency of insertion of $N$ and $s$, the new
effects $N$ are also observed. Thus, the clients witness the observably
equivalent new set of effects $N$, and not the old effects $O$. This ensures
atomicity of summarization in the backing store.

>>>>

Compared to the shim layer, summarization in the backing store is more
complicated. The main challenge is that unlike the shim layer, summarization
cannot run as an atomic operation. Summarization in the backing store involves
deleting previously inserted rows and inserting new rows, where each row
corresponds to an effect. It is essential that concurrent client operations are
permitted, but are not allowed to witness the intermediate state of the
summarization process. To this end, we adopt a summarization strategy that
builds on the causality property of the store. The details of the summarization
are beyond the scope of the paper, and is presented in detail in the tech
report~\cite{}.

### 2014-10-31 motivation.tex
edits

deposit :: [Acc] -> Int -> ((), Maybe Acc)
deposit _ amt = (amt, Just $ Deposit amt)

withdraw :: [Acc] -> Int -> (Bool, Maybe Acc)
withdraw ctxt v =
	if sel1 $ getBalance ctxt () >= v
  then (True, Just $ Withdraw v)
	else (False, Nothing)
\end{codehaskell}
\label{Definition of a bank account expressed in Quelea.}
\label{fig:ex}
\end{figure}

>>>>

deposit :: [Acc] -> Int -> ((), Maybe Acc)
deposit _ amt = (amt, Just dollar Deposit amt)

withdraw :: [Acc] -> Int -> (Bool, Maybe Acc)
withdraw ctxt v =
	if sel1 dollar getBalance ctxt () >= v
  then (True, Just dollar Withdraw v)
	else (False, Nothing)
\end{codehaskell}
\label{Definition of a bank account expressed in Quelea.}
\label{fig:ex}
\end{figure}

### 2014-10-31 transactions.tex
edits

\noindent \begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
save amt =
  x <- $(classify psi1)
  atomically x $ do
    b <- withdraw c amt
    when b $ deposit s amt
\end{codehaskell}
\end{minipage}
\begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
totalBalance =
  x <- $(classify psi2)
  atomically x $ do
    b1 <- getBalance s
    b2 <- getBalance s
    return b1 + b2
\end{codehaskell}
\end{minipage}

>>>>

\noindent \begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
save amt =
  x <- dollar(classify $\psi_1$)
  atomically x dollar do
    b <- withdraw c amt
    when b dollar deposit s amt
\end{codehaskell}
\end{minipage}
\begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
totalBalance =
  x <- dollar(classify $\psi_2$)
  atomically x dollar do
    b1 <- getBalance s
    b2 <- getBalance s
    return b1 + b2
\end{codehaskell}
\end{minipage}
